### 2020-12-03 AISTATS2021_Author_Response_Pack/aistats2021_author_response.tex
edit

	\textbf{Response to R2.} We thank the reviewer for providing detailed feedback.
	Response to questions under Section 8.
	\textbf{(i)}
	In the over-parametrized regime, the minimum solution of $f(A ,B)$ (equation 1) reduces to single-task learning  (cf. Proposition 1 in Wu et al., 20).
	Hence, studing this regime is problematic without adding explicit regularization or implicit algorithmic biases.
	These are interesting research questions, but beyond the scope of our work.

@@

	\textbf{Response to R3.}
	We thank the reviewer for the encouraging review.
	Regarding the question of how the prediction loss varies with $r$, we would like to point out that in the setting of Theorem 2.1, our result implies the following simple corollary.
	Suppose that the singular values of ${B^{\star}}^{\top}\Sigma B^{\star}$ are $\lambda_1, \lambda_2, \dots, \lambda_t$ in decreasing order.
	If we increase $r$ by $1$, the bias reduces by $\lambda_{r+1}$ while the variance increases, the amount of which depends on the singular vector of  ${B^{\star}}^{\top}\Sigma B^{\star}$ corresponding to $\lambda_{r+1}$.
	As an example of this corollary, we can show that in the setting of Example 2.2, the average prediction loss of all tasks is minimized when $r$ is one.
	We also thank the reviewer for suggesting the related work.
	Our work is heavily inspired by Hastie et al., 2019.
	We will add these related work to the next version of the paper.

	\textbf{Response to R5.}
\end{document}

>>>>

	\textbf{Response to R2.} We thank the reviewer for providing detailed feedback.
	Response to questions under Section 8.
	\textbf{(i)}
	In the over-parametrized regime, the minimum solution of $f(A ,B)$ (equation 1) reduces to single-task learning  (cf. Proposition 1 in Wu et al., 2020).
	Hence, studing this regime is problematic without adding explicit regularization or implicit algorithmic biases.
	These are interesting research questions, but beyond the scope of our work.

@@

	\textbf{Response to R3.}
	We thank the reviewer for the encouraging review.
	Regarding the question of how the prediction loss varies with $r$, we would like to point out that in the setting of Theorem 2.1, our result implies the following simple corollary.
	Suppose that the singular values of ${B^{\star}}^{\top}\Sigma B^{\star}$ are $\lambda_1, \lambda_2, \dots, \lambda_t$ in decreasing order.
	If we increase $r$ by $1$, the bias reduces by $\lambda_{r+1}$ while the variance increases, the amount of which depends on the singular vector of  ${B^{\star}}^{\top}\Sigma B^{\star}$ corresponding to $\lambda_{r+1}$.
	As an example of this corollary, we can show that in the setting of Example 2.2, the average prediction loss of all tasks is minimized when $r$ is one.
	We also thank the reviewer for suggesting the related work (indeed our work has been heavily inspired by Hastie et al., 2019).
	We will add these related work to the next version of the paper.

	\textbf{Response to R5.}
	In response to the reviewer's comments, we explain the high-level purpose of our work and the importance of why one should care about analyzing the sample size ratios.
	(1) Hard parameter sharing is a widely used empirical approach to performing multi-task learning.
	(2) However, there remain critical challenges of applying hard parameter sharing successfully in practice.
	The first challenge is negative transfer -- this occurs commonly
\end{document}
